% Candy Auction - Student Data Collection Worksheet
% Algebra 2 - Price vs Demand
\documentclass[11pt]{article}

% Package imports
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{titlesec}

% Formatting
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt}
\setlist[enumerate]{leftmargin=*, itemsep=2pt, topsep=2pt}
\setlength{\parindent}{0pt}
\renewcommand{\arraystretch}{1.6}

% Document begins
\begin{document}

% Header
\begin{center}
  {\LARGE\textbf{Candy Auction Data Collection}}\\[6pt]
  \textbf{Group Members:} \rule{0.25\textwidth}{0.4pt} \rule{0.25\textwidth}{0.4pt} \rule{0.25\textwidth}{0.4pt}\\[4pt]
  \rule{0.25\textwidth}{0.4pt} \quad \textbf{Period:} \rule{0.08\textwidth}{0.4pt} \quad \textbf{Date:} \rule{0.15\textwidth}{0.4pt}
\end{center}

\vspace{0.3em}
\hrule height 0.8pt
\vspace{0.5em}

% Quick Setup
\section*{Quick Setup}
\begin{itemize}
  \item Your group has \textbf{\$20 virtual dollars} to spend (track this yourselves)
  \item Each round: 5 candies are auctioned at a set price
  \item Decide as a group: Will you buy at that price? (You can only buy ONE set per round)
  \item Record the price and how many total groups bought
\end{itemize}

% Data Table
\section*{Data Collection}

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\rowcolor{gray!20}
\textbf{Round} & \textbf{Price for} & \textbf{Number of Groups} & \textbf{Revenue} \\
\rowcolor{gray!20}
 & \textbf{5 Candies (\$)} & \textbf{Buying} & \textbf{(Price × Quantity)} \\
\hline
1 & & & \\
\hline
2 & & & \\
\hline
3 & & & \\
\hline
4 & & & \\
\hline
5 & & & \\
\hline
6 & & & \\
\hline
7 & & & \\
\hline
8 & & & \\
\hline
\end{tabular}
\end{center}

\vspace{0.5em}

% Budget Tracking
\textbf{Budget Tracker:} Starting: \$20.00 \quad Remaining: \rule{1.5cm}{0.4pt}

\vspace{0.5em}

% Desmos Section - Part 1
\section*{Desmos Analysis - Part 1: Enter Data \& Plot}

\textbf{Step 1: Create your price list}

In Desmos, type exactly: \quad \colorbox{gray!20}{\texttt{P = [}} \rule{4cm}{0.4pt} \colorbox{gray!20}{\texttt{]}}

\textit{Example:} \texttt{P = [8, 2, 5, 1, 6.5, 3.5]} \quad (use YOUR prices from the table)

\vspace{0.5em}

\textbf{Step 2: Create your quantity list}

In Desmos, type exactly: \quad \colorbox{gray!20}{\texttt{Q = [}} \rule{4cm}{0.4pt} \colorbox{gray!20}{\texttt{]}}

\textit{Example:} \texttt{Q = [0, 4, 2, 4, 1, 3]} \quad (use YOUR quantities from the table)

\vspace{0.5em}

\textbf{Step 3: Create scatter plot}

In Desmos, type exactly: \quad \colorbox{gray!20}{\texttt{(P, Q)}}

\vspace{0.3em}
✓ Check: You should see dots on the graph showing your data points!

\vspace{0.8em}

% Desmos Section - Part 2
\section*{Desmos Analysis - Part 2: Find the Pattern}

\textbf{Step 4: Add the regression line}

In a new line, type exactly: \quad \colorbox{gray!20}{\texttt{Q \textasciitilde{} m*P + b}}

\vspace{0.3em}
\textit{Note: The} \textasciitilde{} \textit{symbol tells Desmos to find the best fit line}

\vspace{0.5em}

\textbf{Step 5: Record what Desmos found}

Desmos will show values for $m$ and $b$. Write them here:

\begin{center}
\framebox{
\begin{minipage}{0.7\textwidth}
\vspace{0.5em}
\centering
{\large $Q = $ \framebox[2cm]{\rule{0pt}{0.8em}\hspace{2cm}} $\times P + $ \framebox[2cm]{\rule{0pt}{0.8em}\hspace{2cm}}}

\vspace{0.3em}
\small (slope $m$) \hspace{3cm} (y-intercept $b$)
\vspace{0.3em}
\end{minipage}
}
\end{center}

\vspace{0.8em}

% Quick Questions
\section*{Quick Analysis}

\begin{enumerate}
  \item Is your slope negative (going down left to right)? \quad $\square$ Yes \quad $\square$ No
  
  \vspace{0.3em}
  \item In one sentence: What does a negative slope mean about price and demand?
  
  \vspace{0.2em}
  \rule{\textwidth}{0.4pt}
  
  \vspace{0.3em}
  \item Which price in your table gave the highest revenue? \$\rule{1.5cm}{0.4pt}
  
  \vspace{0.3em}
  \item Prediction: Using your equation, how many groups would buy if the price was \$4.00?
  
  \vspace{0.2em}
  Show work: \rule{0.3\textwidth}{0.4pt} groups
\end{enumerate}

\vspace{0.5em}

% Footer
\hrule height 0.4pt
\begin{center}
  \small\textit{Save your Desmos graph! Screenshot or bookmark the link - you'll need it tomorrow.}
\end{center}

\end{document}